---
title: "Progress report 1"
bibliography: ../../library/imap.bib
date: 'Updated: `r Sys.time()`'
output:
  html_document:
    css: ../../code/css/report.css
    output_file: "../../reports/report1.html"
    # keep_md: yes
link-citations: yes
subtitle: Metadata profiling
biblio-style: apalike

---


<br>

## Preamble
* Load Metadata
	* Inspect the metadata column names.
	* Remove number sign at the name of column one.
	* Note that Var1 starts at index 7.
	* Select important variables for downstream analysis.
	* Define each categoric variable as factor.

```{r echo=TRUE}
# Load samplemetadata
samplemetadata <- readr::read_table2(file="../../data/metadata/samplemetadata.tsv", col_names = T)
colnames(samplemetadata)[1] <- "SampleID"

# View column names
names(samplemetadata)

# Define categoric variables like
samplemetadata$SampleID <- as.factor(samplemetadata$SampleID)
samplemetadata$Var1 <- as.factor(samplemetadata$Var1)
samplemetadata$Var2 <- as.factor(samplemetadata$Var2)
samplemetadata$Var3 <- as.factor(samplemetadata$Var3)
samplemetadata$Var4 <- as.factor(samplemetadata$Var4)

# Add more variables as needed
```

<br>
<br>


### Status of sample metadata

```{r, include=FALSE}
metadatastatus <- funModeling::df_status(samplemetadata)
```

The following script (disabled) requires kableExtra package. Installation doesn't work in docker container but can be installed directly from R or RStudio.
```{r dfstatus}
library(dplyr)
library(knitr)
library(kableExtra)

# show data
metadatastatus %>% kable() %>% kable_styling(bootstrap_options = "bordered", full_width = F)
```

#Key: **q_zeros**: quantity of missing data; **p_zeros**: percentage of missing data, **q_na**: quantity of NA; **p_na**: percentage of NA, **q_inf**: quantity of infinite values; **p_inf**: percentage of infinity values,  **type**: factor, character, integer or numeric; **unique**: levels of the variable.

<br>

<br>
<br>


### Selected variables for downsteam analysis
> This is important for mapping to output from dowmstream analysis

```{r, include=FALSE}
library(dplyr)
variables <- samplemetadata %>% dplyr::select("SampleID", "Var1", "Var2", "Var3", "Var4")

# Confirm variable names
names(variables)

# Define variables
variables$SampleID <- as.factor(variables$SampleID)
variables$Var1 <- as.factor(variables$Var1)
variables$Var2 <- as.factor(variables$Var2)
variables$Var3 <- as.factor(variables$Var3)
variables$Var4 <- as.factor(variables$Var4)

varstatus <- funModeling::df_status(variables)
```

```{r message=FALSE, warning=FALSE}
library(dplyr)
library(knitr)
library(kableExtra)

# show variable status
varstatus %>% kable() %>% kable_styling(bootstrap_options = "bordered", full_width = FALSE)

```

Key: **q_zeros**: quantity of missing data; **p_zeros**: percentage of missing data, **q_na**: quantity of NA; **p_na**: percentage of NA, **q_inf**: quantity of infinite values; **p_inf**: percentage of infinity values,  **type**: factor, character, integer or numeric; **unique**: frequency of the values.

<br>
<br>

## View variable levels (first 5 rows)

```{r message=FALSE, warning=FALSE}
library(kableExtra)

variables %>% head(5)  %>% kable() %>% kable_styling(bootstrap_options = "bordered", full_width = FALSE)
```

<br>
<hr>
<br>

## Frequency of experimental variables

```{r varfreq, fig.height=8, fig.width=8, message=FALSE, warning=FALSE}
library(ggplot2)

# Var1
var1histplot <- ggpubr::gghistogram(variables, x = "Var1", stat="count", fill = "#ff0000") + 
  labs(x = "Variable 1", y = "Sample count") 
  
# Var2
var2histplot <- ggpubr::gghistogram(variables, x = "Var2", stat="count", fill = "#00ff00") + 
  labs(x = "Variable 2", y = "Sample count") 

# Var3
var3histplot <- ggpubr::gghistogram(variables, x = "Var3", stat="count", fill = "#0000ff") + 
  theme(axis.text.x=element_text(angle = 0, hjust = 0))+ scale_y_continuous(labels=scaleFUN) +
  labs(x = "Variable 3", y = "Sample count") 

ggpubr::ggarrange(var1histplot,var2histplot, var3histplot, ncol = 1, nrow = 3, align = "hv", labels = c("AUTO"))
```

<br>

### Profiling metadata used in the iMAP casestudy
> Using the Casestudy metadata located in this path: iMAP/resources/metadata/samplemetadata_casestudy.tsv

```{r casestudymetdat, echo=TRUE}
library("dplyr")
library("knitr")

# Load samplemetadata

samplemetadata2 <- readr::read_table2(file="../../data/metadata/samplemetadata_casestudy.tsv", col_names = T)
samplemetadata2 <- samplemetadata2[, -7]
colnames(samplemetadata2)[1] <- "SampleID"

# View column names
names(samplemetadata2)

# Define categoric variables like
samplemetadata2$SampleID <- as.factor(samplemetadata2$SampleID)
samplemetadata2$Sex <- as.factor(samplemetadata2$Sex)
samplemetadata2$Time <- as.factor(samplemetadata2$Time)
samplemetadata2$DayID <- as.factor(samplemetadata2$DayID)
samplemetadata2$DPW <- as.factor(samplemetadata2$DPW)

# Add more variables as needed

variables2 <- samplemetadata2  %>% dplyr::select("SampleID", "Sex", "Time", "DayID", "DPW" )

```

## Status of custom metadata

<br>

```{r, include = FALSE}
varstatus2 <- funModeling::df_status(variables2)
```

```{r message=FALSE, warning=FALSE}
library(dplyr)
library(knitr)
library(kableExtra)

# show data
varstatus2 %>% kable() %>% kable_styling(bootstrap_options = "bordered", full_width = FALSE) 
```


Key: **q_zeros**: quantity of missing data; **p_zeros**: percentage of missing data, **q_na**: quantity of NA; **p_na**: percentage of NA, **q_inf**: quantity of infinite values; **p_inf**: percentage of infinity values,  **type**: factor, character, integer or numeric; **unique**: levels of the variable.


When reviewing metadata status you may notice that numeric variables are confused with numeric data. For example, variable **DPW** (days post weaning) on Table x shows 12 missing values (3.33%) which is incorrect. As investigators we know that day 1 was coded zero (0) (12 zeros for 12 mouse) which in descriptive statistics is interpreted as missing data. To correct this we re-coded the samples with unique identifies shown as DayID to distinguish them from integers. However, depending of experiment this kind of variables need to be converted to character during analysis. 

<br>
<br>

## Frequency of experimental variables in the Demo dataset

```{r varfreq2, fig.height=8, fig.width=8, message=FALSE, warning=FALSE}
library(ggplot2)
#sort by dpw (descending)

sexhistplot <- ggpubr::gghistogram(variables2, x = "Sex", stat="count", fill = "#ff0000") + 
  labs(x = "Sex of animal", title = "Sex variable")

timehistplot <- ggpubr::gghistogram(variables2, x = "Time", stat="count", fill = "#00ff00") + 
  labs(x = "Time of Weaning", title = "Time variable")

dpwhistplot <- ggpubr::gghistogram(variables2, x = "DayID", stat="count", fill = "#0000ff") +
  theme(axis.text.x=element_text(angle = 90, hjust = 0))+ scale_y_continuous(labels=scaleFUN) + 
  labs(x = "Day Code", title = "Sex variable")

ggpubr::ggarrange(sexhistplot,timehistplot, dpwhistplot, ncol = 1, nrow = 3,  common.legend = TRUE, legend = "top", align = "hv", labels = c(""))
```


```{r}

save(samplemetadata, samplemetadata2, variables, variables2, file = "metadatavars.RData")
```

<br>
<hr>
<br>

## Posible questions

<br>

### Metadata profiling 


* QN1: Are there samples to be removed from the analysis based on their count?
* QN2: Are there enough variables for downstream diversity and statistical analysis?
* QN3: .......?
* QN4: .......?
* QN5: .......?

<br>

## Summary of packages used in the analysis
```{r}
sessionInfo()
```

<br>

