---
output:
  html_document: default
bibliography: ["../../library/imap.bib"]
biblio-style: apalike
link-citations: yes
date: "Updated: `r Sys.time()`"

---

```{r child='00_00_global_setup.Rmd'}

```

```{r}
load("../../results/tables/phylotype/otutaxon.RData")
```

## Heatmaps

<hr>

### Phyla

```{r p_heatmap, fig.height=6, fig.width=10}
library(reshape2) # for melt

ggplot(melt(p.scaled.t), aes(x=Var1, y=Var2, fill=value)) + 
  geom_tile(mapping = NULL, data = NULL, stat = "identity",
  position = "identity", na.rm = TRUE,inherit.aes = TRUE)+
  scale_fill_gradient2(low = c("blue","blue4"), high = c("red", "red"), na.value = "white", name  ="Scaled abund") + theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  labs(x="Samples (n = 8)", y="") + theme(axis.text.y = element_text(face = "italic", size = 10))

```

<br>

### Class

```{r c_heatmap, fig.height=8, fig.width=10}
library(reshape2) # for melt
ggplot(melt(c.scaled.t), aes(x=Var1, y=Var2, fill=value)) + 
  geom_tile(mapping = NULL, data = NULL, stat = "identity",
  position = "identity", na.rm = TRUE,inherit.aes = TRUE)+
  scale_fill_gradient2(low = c("blue","blue4"), high = c("red", "red"), na.value = "white", name  ="Scaled abund") + theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  labs(x="Samples (n = 8)", y="") + theme(axis.text.y = element_text(face = "italic", size = 10))
```

<br>

### Order

```{r o_heatmap, fig.height=8, fig.width=10}
library(reshape2) # for melt
ggplot(melt(o.scaled.t), aes(x=Var1, y=Var2, fill=value)) + 
  geom_tile(mapping = NULL, data = NULL, stat = "identity",
  position = "identity", na.rm = TRUE,inherit.aes = TRUE)+
  scale_fill_gradient2(low = c("blue","blue4"), high = c("red", "red"), na.value = "white", name  ="Scaled abund") + theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  labs(x="Samples (n = 8)", y="") + theme(axis.text.y = element_text(face = "italic", size = 10))
```

<br>

### Family

```{r f_heatmap, fig.height=12, fig.width=10}
library(reshape2) # for melt
ggplot(melt(f.scaled.t), aes(x=Var1, y=Var2, fill=value)) + 
  geom_tile(mapping = NULL, data = NULL, stat = "identity",
  position = "identity", na.rm = TRUE,inherit.aes = TRUE)+
  scale_fill_gradient2(low = c("blue","blue4"), high = c("red", "red"), na.value = "white", name  ="Scaled abund") + theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  labs(x="Samples (n = 8)", y="") + theme(axis.text.y = element_text(face = "italic", size = 10))
```

<br>

### Genus

```{r g_heatmap, fig.height=16, fig.width=10}
library(reshape2) # for melt
ggplot(melt(g.scaled.t), aes(x=Var1, y=Var2, fill=value)) + 
  geom_tile(mapping = NULL, data = NULL, stat = "identity",
  position = "identity", na.rm = TRUE,inherit.aes = TRUE)+
  scale_fill_gradient2(low = c("blue","blue4"), high = c("red", "red"), na.value = "white", name  ="Scaled abund") + theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  labs(x="Samples (n = 8)", y="") + theme(axis.text.y = element_text(face = "italic", size = 10))
```

<br>

## PAM clustering

<hr>

* Partitioning Around Medoids (PAM)
* Is considered to be the more robust version of K-means.
* Medoids	are representative objects of the cluster.
* Starts by determining the best number of clusters using factoextra::fviz_nbclust()
* Method: Silhouette
* Metric = Euclidean
* Robust for partitioning data set into clusters of observation.
* User are required to know the data to indicate the appropriate number of clusters to be produced. 
* Visualize clusters (pam results) using factoextra::fviz_cluster()

<br>

### Number of best clusters

<br>

```{r bestclusters}
library(NbClust)
otu.nbclust <- NbClust(otu.scaled.t, distance = "euclidean", min.nc=2, max.nc=3, method = "average", index = "ch")
p.nbclust <- NbClust(p.scaled.t, distance = "euclidean", min.nc=2, max.nc=3, method = "average", index = "ch")
c.nbclust <- NbClust(c.scaled.t, distance = "euclidean", min.nc=2, max.nc=3, method = "average", index = "ch")
o.nbclust <- NbClust(o.scaled.t, distance = "euclidean", min.nc=2, max.nc=3, method = "average", index = "ch")
f.nbclust <- NbClust(f.scaled.t, distance = "euclidean", min.nc=2, max.nc=3, method = "average", index = "ch")
g.nbclust <- NbClust(g.scaled.t, distance = "euclidean", min.nc=2, max.nc=3, method = "average", index = "ch")

cat("OTUbased\n") 
print (otu.nbclust$Best.nc)
# fviz_nbclust(otu.nbclust) # Same output

cat("Phylum\n") 
print (p.nbclust$Best.nc)

cat("Class\n") 
print (c.nbclust$Best.nc)

cat("Order\n") 
print (o.nbclust$Best.nc)

cat("Family\n") 
print (f.nbclust$Best.nc)

cat("Genus\n") 
print (g.nbclust$Best.nc)
```

<br>

### Visualization of best clusters

```{r fviznbclust, eval=FALSE, fig.height=6, fig.width=10, message=FALSE, warning=FALSE, include=FALSE}
library(cluster)
library(factoextra)

# Raw abundance

otu_nbcluster1 <- factoextra::fviz_nbclust(otu.scaled.t, pam, method = "silhouette")+ labs(x="OTU clusters", title = "") + theme_classic()
p_nbcluster1 <- factoextra::fviz_nbclust(p.scaled.t, pam, method = "silhouette")+ labs(x="Phylum clusters", title = "") + theme_classic()
c_nbcluster1 <- factoextra::fviz_nbclust(c.scaled.t, pam, method = "silhouette")+ labs(x="Class clusters", title = "") + theme_classic()
o_nbcluster1 <- factoextra::fviz_nbclust(o.scaled.t, pam, method = "silhouette")+ labs(x="Order clusters", title = "") + theme_classic()
f_nbcluster1 <- factoextra::fviz_nbclust(f.scaled.t, pam, method = "silhouette")+ labs(x="Family clusters", title = "") + theme_classic()
g_nbcluster1 <- factoextra::fviz_nbclust(g.scaled.t, pam, method = "silhouette")+ labs(x="Genus clusters", title = "") + theme_classic()

ggpubr::ggarrange(otu_nbcluster1, p_nbcluster1, c_nbcluster1, o_nbcluster1, f_nbcluster1, g_nbcluster1, ncol = 3, nrow = 2,  common.legend = FALSE, legend = "none", align = "hv", labels = "")

```

Figure x: Optimal number of OTU clusters. The suggested number of best clusters (dotted line) that could explain most variation is 2 for OTUs (A), 3 for phylum (B), 3 for class (C), 2 for Order (D), 10 for Family (E) and 2 for Genus (F). A high average Silhouette width indicates high quality clustering.



<br>

### Cluster validation
<!-- * Using Silhouette Information -->
<!-- * Use original data (non-matrices) -->
<!-- * Measures how well a cluster is -->
<!-- * Estimates the average distance between clusters. -->

```{r fviz_silhouette, fig.height=10, fig.width=10, message=FALSE, warning=FALSE}

otu.pam.t <- pam(otu.t, 2, metric = "euclidean", stand = FALSE)
p.pam.t <- pam(phylum.t, 2, metric = "euclidean", stand = FALSE)
c.pam.t <- pam(class.t, 2, metric = "euclidean", stand = FALSE)
o.pam.t <- pam(order.t, 2, metric = "euclidean", stand = FALSE)
f.pam.t <- pam(family.t,2, metric = "euclidean", stand = FALSE)
g.pam.t <- pam(genus.t, 2, metric = "euclidean", stand = FALSE)

# Visualize pam
otu.fviz.t <- factoextra::fviz_silhouette(otu.pam.t, diss=FALSE, 2) + ggtitle("OTUs")+ normalaxislayout2 + xlab("Data point") + ylab("Si width")
p.fviz.t <- factoextra::fviz_silhouette(p.pam.t, diss=FALSE, 3) + ggtitle("Phylum")+ normalaxislayout2 + xlab("Data point") + ylab("Si width")
c.fviz.t <- factoextra::fviz_silhouette(c.pam.t, diss=FALSE, 3) + ggtitle("Class")+ normalaxislayout2 + xlab("Data point") + ylab("Si width")
o.fviz.t <- factoextra::fviz_silhouette(o.pam.t, diss=FALSE, 2) + ggtitle("Order")+ normalaxislayout2 + xlab("Data point") + ylab("Si width") 
f.fviz.t <- factoextra::fviz_silhouette(f.pam.t, diss=FALSE, 2) + ggtitle("Family")+ normalaxislayout2 + xlab("Data point") + ylab("Si width") 
g.fviz.t <- factoextra::fviz_silhouette(g.pam.t, diss=FALSE, 2) + ggtitle("Genus")+ normalaxislayout2 + xlab("Data point") + ylab("Si width") 


ggpubr::ggarrange(otu.fviz.t, p.fviz.t, c.fviz.t, o.fviz.t, f.fviz.t, g.fviz.t, ncol = 2, nrow = 3,  common.legend = FALSE, legend = "none", align = "hv", labels = "")

```

Figure x: Silhouette plot guided by the best number of clusters. Observations with a large Si (almost 1) are very well clustered. A small Si (around 0) means that the observation lies between two clusters while a negative Si are probably placed in the wrong cluster.

<br>

### Cluster visualization
```{r sampleclusters, fig.height=10, fig.width=10}
pam1 <- factoextra::fviz_cluster(otu.pam.t, 
             palette = c("#00AFBB", "#FC4E07"), # color palette
             ellipse.type = "convex", # Concentration ellipse
             ellipse.level = 0.95,
             stand = FALSE,
             axes = c(1,2),
             pointsize = 2,
             geom = c("point", ""),
             repel = FALSE, # Avoid label overplotting (slow)
             ggtheme = theme_classic()
             ) + ggplot2::ggtitle("") + normalaxislayout + ggtitle("OTUs")

pam2 <- factoextra::fviz_cluster(p.pam.t, 
             palette = c("#00AFBB", "#FC4E07"), # color palette
             ellipse.type = "convex", # Concentration ellipse
             ellipse.level = 0.95,
             stand = FALSE,
             axes = c(1,2),
             pointsize = 2,
             geom = c("point", ""),
             repel = FALSE, # Avoid label overplotting (slow)
             ggtheme = theme_classic()
             ) + ggplot2::ggtitle("") + normalaxislayout + ggtitle("Phylum")

pam3 <- factoextra::fviz_cluster(c.pam.t, 
             palette = c("#00AFBB", "#FC4E07"), # color palette
             ellipse.type = "convex", # Concentration ellipse
             ellipse.level = 0.95,
             stand = FALSE,
             axes = c(1,2),
             pointsize = 2,
             geom = c("point", ""),
             repel = FALSE, # Avoid label overplotting (slow)
             ggtheme = theme_classic()
             ) + ggplot2::ggtitle("") + normalaxislayout + ggtitle("Class")

pam4 <- factoextra::fviz_cluster(o.pam.t, 
             palette = c("#00AFBB", "#FC4E07"), # color palette
             ellipse.type = "convex", # Concentration ellipse
             ellipse.level = 0.95,
             stand = FALSE,
             axes = c(1,2),
             pointsize = 2,
             geom = c("point", ""),
             repel = FALSE, # Avoid label overplotting (slow)
             ggtheme = theme_classic()
             ) + ggplot2::ggtitle("") + normalaxislayout + ggtitle("Order")

pam5 <- factoextra::fviz_cluster(f.pam.t, 
             palette = c("#00AFBB", "#FC4E07"), # color palette
             ellipse.type = "convex", # Concentration ellipse
             ellipse.level = 0.95,
             stand = FALSE,
             axes = c(1,2),
             pointsize = 2,
             geom = c("point", ""),
             repel = FALSE, # Avoid label overplotting (slow)
             ggtheme = theme_classic()
             ) + ggplot2::ggtitle("") + normalaxislayout + ggtitle("Family")

pam6 <- factoextra::fviz_cluster(g.pam.t, 
             palette = c("#00AFBB", "#FC4E07"), # color palette
             ellipse.type = "convex", # Concentration ellipse
             ellipse.level = 0.95,
             stand = FALSE,
             axes = c(1,2),
             pointsize = 2,
             geom = c("point", ""),
             repel = FALSE, # Avoid label overplotting (slow)
             ggtheme = theme_classic()
             ) + ggplot2::ggtitle("") + normalaxislayout + ggtitle("Genus")

ggpubr::ggarrange(pam1, pam2, pam3, pam4, pam5, pam6, ncol = 2, nrow = 3,  common.legend = FALSE, legend = "none", align = "hv", labels = "")
```

<br>
<br>

### Number of best clusters
* Range: Shown sequencially for OTU, Phylum, Class. Order, Family and Genus
```{r fviz_silhouette_intext, eval=FALSE, fig.height=8, fig.width=10, message=FALSE, warning=FALSE, include=FALSE}
# <!-- ########################## -->
# <!-- ########################## -->
# <!-- ########################## -->
# <!-- ########################## -->

### Cluster validation for Day3

otu.pam.t <- pam(otu.t, 2, metric = "euclidean", stand = FALSE)
p.pam.t <- pam(phylum.t, 2, metric = "euclidean", stand = FALSE)
c.pam.t <- pam(class.t, 2, metric = "euclidean", stand = FALSE)
o.pam.t <- pam(order.t, 2, metric = "euclidean", stand = FALSE)
f.pam.t <- pam(family.t, 2, metric = "euclidean", stand = FALSE)
g.pam.t <- pam(genus.t, 2, metric = "euclidean", stand = FALSE)

# Visualize pam
otu.fviz.t <- factoextra::fviz_silhouette(otu.pam.t) + ggplot2::ggtitle("OTUs")+ normalaxislayout2 + labs(x = "Sample ID", y = "Si width")#+ noxlabels 
p.fviz.t <- factoextra::fviz_silhouette(p.pam.t) + ggplot2::ggtitle("Phylum")+ normalaxislayout2 + labs(x = "Sample ID", y = "Si width")#+ noxlabels 
c.fviz.t <- factoextra::fviz_silhouette(c.pam.t) + ggplot2::ggtitle("Class")+ normalaxislayout2 + labs(x = "Sample ID", y = "Si width")#+ noxlabels 
o.fviz.t <- factoextra::fviz_silhouette(o.pam.t) + ggplot2::ggtitle("Order")+ normalaxislayout2 + labs(x = "Sample ID", y = "Si width")#+ noxlabels 
f.fviz.t <- factoextra::fviz_silhouette(f.pam.t) + ggplot2::ggtitle("Family")+ normalaxislayout2 + labs(x = "Sample ID", y = "Si width")#+ noxlabels  
g.fviz.t <- factoextra::fviz_silhouette(g.pam.t) + ggplot2::ggtitle("Genus")+ normalaxislayout2 + labs(x = "Sample ID", y = "Si width")#+ noxlabels 


ggpubr::ggarrange(otu.fviz.t, p.fviz.t, c.fviz.t, o.fviz.t, f.fviz.t, g.fviz.t, ncol = 2, nrow = 3,  common.legend = FALSE, legend = "none", align = "hv", labels = "")
```

`

<br>

```{r eval=FALSE, fig.height=8, fig.width=10, message=FALSE, warning=FALSE, include=FALSE}
library(vegan)

# <br>


pam1 <- factoextra::fviz_cluster(otu.pam.t, 
             palette = c("#00AFBB", "#FC4E07"), # color palette
             ellipse.type = "convex", # Concentration ellipse
             ellipse.level = 0.95,
             main = "Cluster plot", 
             stand = FALSE,
             axes = c(1,2),
             pointsize = 2,
             geom = c("point", ""),
             repel = FALSE, # Avoid label overplotting (slow)
             ggtheme = theme_classic()
             ) + ggplot2::ggtitle("") + normalaxislayout + ggtitle("OTUs")

pam2 <- factoextra::fviz_cluster(p.pam.t, 
             palette = c("#00AFBB", "#FC4E07"), # color palette
             ellipse.type = "convex", # Concentration ellipse
             ellipse.level = 0.95,
             main = "Cluster plot",
             stand = FALSE,
             axes = c(1,2),
             pointsize = 2,
             geom = c("point", ""),
             repel = FALSE, # Avoid label overplotting (slow)
             ggtheme = theme_classic()
             ) + ggplot2::ggtitle("") + normalaxislayout + ggtitle("Phylum")

pam3 <- factoextra::fviz_cluster(c.pam.t, 
             palette = c("#00AFBB", "#FC4E07"), # color palette
             ellipse.type = "convex", # Concentration ellipse
             ellipse.level = 0.95,
             stand = FALSE,
             axes = c(1,2),
             pointsize = 2,
             geom = c("point", ""),
             repel = FALSE, # Avoid label overplotting (slow)
             ggtheme = theme_classic()
             ) + ggplot2::ggtitle("") + normalaxislayout + ggtitle("Class")

pam4 <- factoextra::fviz_cluster(o.pam.t, 
             palette = c("#00AFBB", "#FC4E07"), # color palette
             ellipse.type = "convex", # Concentration ellipse
             ellipse.level = 0.95,
             stand = FALSE,
             axes = c(1,2),
             pointsize = 2,
             geom = c("point", ""),
             repel = FALSE, # Avoid label overplotting (slow)
             ggtheme = theme_classic()
             ) + ggplot2::ggtitle("") + normalaxislayout + ggtitle("Order")

pam5 <- factoextra::fviz_cluster(f.pam.t, 
             palette = c("#00AFBB", "#FC4E07"), # color palette
             ellipse.type = "convex", # Concentration ellipse
             ellipse.level = 0.95,
             stand = FALSE,
             axes = c(1,2),
             pointsize = 2,
             geom = c("point", ""),
             repel = FALSE, # Avoid label overplotting (slow)
             ggtheme = theme_classic()
             ) + ggplot2::ggtitle("") + normalaxislayout + ggtitle("Family")

pam6 <- factoextra::fviz_cluster(g.pam.t, 
             palette = c("#00AFBB", "#FC4E07", "black"), # color palette
             ellipse.type = "convex", # Concentration ellipse
             ellipse.level = 0.95,
             stand = FALSE,
             axes = c(1,2),
             pointsize = 2,
             geom = c("point", ""),
             repel = FALSE, # Avoid label overplotting (slow)
             ggtheme = theme_classic()
             ) + ggplot2::ggtitle("") + normalaxislayout + ggtitle("Genus")

ggpubr::ggarrange(pam1, pam2, pam3, pam4, pam5, pam6, ncol = 2, nrow = 3,  common.legend = FALSE, legend = "none", align = "hv", labels = "")

# <!-- ########################### -->
# <!-- ########################### -->
# <!-- ########################### -->
# <!-- ########################### -->
```


<br>

## PCA (Principal Component Analysis)

<hr>

* Identifies smaller number of uncorrelated variables (principal components) from a large set of data. 
* Explains the maximum amount of variance with the minimum number of principal components. 
* Missing values are replaced by the column mean
* Use scree plot to estimate which components explain most of the variability in the data

```{r pca}
otu.pca <- FactoMineR::PCA(otu.t, scale.unit = FALSE, graph = FALSE)
p.pca <- FactoMineR::PCA(phylum.t, scale.unit = FALSE, graph = FALSE)
c.pca <- FactoMineR::PCA(class.t, scale.unit = FALSE, graph = FALSE)
o.pca <- FactoMineR::PCA(order.t, scale.unit = FALSE, graph = FALSE)
f.pca <- FactoMineR::PCA(family.t, scale.unit = FALSE, graph = FALSE)
g.pca <- FactoMineR::PCA(genus.t, scale.unit = FALSE, graph = FALSE)
```


### Scree plot: Analysis of number of suitable components
```{r fviz_screeplot, fig.height=8, fig.width=10}

otu.scree <- factoextra::fviz_screeplot(otu.pca, xlab = "Dimens ions", ylab = "Explained variance(%)", addlabels = TRUE,  ylim = c(0, 100)) + ggplot2::ggtitle("") + cleanup
p.scree <- factoextra::fviz_screeplot(p.pca, xlab = "Dimens ions", ylab = "Explained variance(%)", addlabels = TRUE,  ylim = c(0, 100)) + ggplot2::ggtitle("") + cleanup
c.scree <- factoextra::fviz_screeplot(c.pca, xlab = "Dimensions", ylab = "Explained variance(%)", addlabels = TRUE, ylim = c(0, 100)) + ggplot2::ggtitle("")  + cleanup
o.scree <- factoextra::fviz_screeplot(o.pca, xlab = "Dimensions", ylab = "Explained variance(%)", addlabels = TRUE, ylim = c(0, 100)) + ggplot2::ggtitle("")  + cleanup
f.scree <- factoextra::fviz_screeplot(f.pca, xlab = "Dimensions", ylab = "Explained variance(%)", addlabels = TRUE, ylim = c(0,100)) + ggplot2::ggtitle("")  + cleanup
g.scree <- factoextra::fviz_screeplot(g.pca, xlab = "Dimensions", ylab = "Explained variance(%)", addlabels = TRUE, ylim = c(0, 100)) + ggplot2::ggtitle("")  + cleanup

multiplot(otu.scree, p.scree, f.scree, c.scree, o.scree, g.scree, cols = 2)
```

Figure x: Scree plot of PCA. Shows which components explain most of the variability in the data. Over 80% of the variances contained in OTU and taxonomy data are retained by the first two principal components. The first PC explains the maximum amount of variation in the data set.

<br>

## PCoA or PCO: Principal Coordinates Analysis 

<hr>

* Similar to PCA but is basically an eigen-analysis of a distance or dissimilarity matrix.
```{r loadings, fig.height=3, fig.width=6, message=FALSE, warning=FALSE}

# load("../../results/tables/phylotype/otutaxon.RData")

pco <- function(dis, k=2)
{
        tmp <-cmdscale(dis,k=k,eig=TRUE)
        class(tmp) <- "pco"
        return(tmp)
}

```

<br>

```{r pcoa, eval=FALSE, fig.height=6, fig.width=10, message=FALSE, warning=FALSE, include=FALSE}
library(vegan)

otu.dis.bray <- vegdist(otu.t, method="bray")
p.dis.bray <- vegdist(phylum.t, method="bray")
c.dis.bray <- vegdist(class.t, method="bray")
o.dis.bray <- vegdist(order.t, method="bray")
f.dis.bray <- vegdist(family.t, method="bray")
g.dis.bray <- vegdist(genus.t, method="bray")

otu.pco <- pco(otu.dis.bray, k=10)
p.pco <- pco(p.dis.bray, k=10)
c.pco <- pco(c.dis.bray, k=10)
o.pco <- pco(o.dis.bray, k=10)
f.pco <- pco(f.dis.bray, k=10)
g.pco <- pco(g.dis.bray, k=10)
# 
# par(cex.axis=1, cex.lab=1.5, cex.main=2, cex.sub=1)
# par(mfrow = c(2, 3))
# barplot(otu.pco$eig, main = "OTUs", xlab = "PCO1", ylab = "PCO2")
# barplot(p.pco$eig, main = "Phylum", xlab = "PCO1", ylab = "PCO2")
# barplot(c.pco$eig, main = "Class", xlab = "PCO1", ylab = "PCO2")
# barplot(o.pco$eig, main = "Order", xlab = "PCO1", ylab = "PCO2")
# barplot(f.pco$eig, main = "Family", xlab = "PCO1", ylab = "PCO2")
# barplot(g.pco$eig, main = "Genus", xlab = "PCO1", ylab = "PCO2") 


plot(otu.pco$points, main = "OTUs", xlab = "PCO1", ylab = "PCO2", col=2)
abline(h=0, v=0, lt=2, col="grey")

plot(p.pco$points, main = "Phylum", xlab = "PCO1", ylab = "PCO2", col=3)
abline(h=0, v=0, lt=2, col="grey")

plot(c.pco$points, main = "Class", xlab = "PCO1", ylab = "PCO2", col=4)
abline(h=0, v=0, lt=2, col="grey")

plot(o.pco$points, main = "Order", xlab = "PCO1", ylab = "PCO2", col=5)
abline(h=0, v=0, lt=2, col="grey")

plot(f.pco$points, main = "Family", xlab = "PCO1", ylab = "PCO2", col=6)
abline(h=0, v=0, lt=2, col="grey")

plot(g.pco$points, main = "Genus", xlab = "PCO1", ylab = "PCO2", col="orange") 
abline(h=0, v=0, lt=2, col="grey")

```

Figure x: Principal coordinate analysis ordination using Bray-Curtis dissimilarity matrix. Objects that are ordinated closer together have smaller dissimilarity values than those ordinated further apart. A successful PCoA will capture most of the variation in the (dis)similarity matrix in a few PCoA axes.


<br>


## NMDS (Non-metric multidimensional scaling)

<hr>

* Goodness of fit and Sheperd plot can be used to determine the good or poor fit. 
* Stress values are used to indicate the quality of NMDS ordination, <0.1 are considered fair, <0.05 indicate good fit.
* [Reference](https://mb3is.megx.net/gustame/dissimilarity-based-methods/nmds)
```{r eval=FALSE, include=FALSE}
set.seed(110912)
library(vegan)

otu.mds <- metaMDS(otu.t, distance = "bray", k=3, try=10, display = c("sites"), choices = c(1, 2), type = "t", shrink = FALSE) # OTU abundance data.
p.mds <- metaMDS(phylum.t, distance = "bray", k=3, try=10, display = c("sites"), choices = c(1, 2), type = "t", shrink = FALSE) # phylum abundance data.
c.mds <- metaMDS(class.t, distance = "bray", k=3, try=10, display = c("sites"), choices = c(1, 2), type = "t", shrink = FALSE) # class abundance data.
o.mds <- metaMDS(order.t, distance = "bray", k=3, try=10, display = c("sites"), choices = c(1, 2), type = "t", shrink = FALSE) # order abundance data.
f.mds <- metaMDS(family.t, distance = "bray", k=3, try=10, display = c("sites"), choices = c(1, 2), type = "t", shrink = FALSE) # family abundance data.
g.mds <- metaMDS(genus.t, distance = "bray", k=3, try=10, display = c("sites"), choices = c(1, 2), type = "t", shrink = FALSE) # genus abundance data.

save(otu.mds,p.mds,c.mds,o.mds,f.mds,g.mds, file = "../../results/mds.RData")
```


```{r}
load(file = "../../results/mds.RData")
```

<br>

### Parameters used for the NMDS

```{r}

cat("\nOTUs\n----------------------------")
otu.mds

cat("\nPhylum\n----------------------------")
p.mds 

cat("\nClass\n----------------------------")
c.mds 

cat("\nOrder\n----------------------------")
o.mds 


cat("\nFamily\n----------------------------")
f.mds 

cat("\nGenus\n----------------------------")
g.mds 

```

<br>

### Sherperd and non-metric multidimensional scaling plots.

```{r stressplot, fig.height=8, fig.width=10}
par(mfrow=c(2,3))
par(cex.axis=1.5, cex.lab=1.8, cex.main=2, cex.sub=1.2)

stressplot(otu.mds)
mtext("OTUs", cex=.8, adj = 0)
stressplot(p.mds)
mtext("Phylum", cex=.8, adj = 0)
stressplot(c.mds)
mtext("Class", cex=.8, adj = 0)
stressplot(o.mds)
mtext("Order", cex=.8, adj = 0)
stressplot(f.mds)
mtext("Family", cex=.8, adj = 0)
stressplot(g.mds)
mtext("Genus", cex=.8, adj = 0)
```

<br><hr>

```{r goodness, fig.height=8, fig.width=10}
par(mfrow=c(2,3))
par(cex.axis=1.5, cex.lab=1.8, cex.main=2, cex.sub=1.2)

gof <- goodness(otu.mds)
plot(otu.mds, display = "species", cex = gof/mean(gof))
points(otu.mds, display = "sites", cex = gof/mean(gof), col=3)
abline(h=0, v=0, lt=2, col="grey")
mtext("OTUs", cex=.8, adj = 0)
text(9, -5, "Stress = 0.11")

gof <- goodness(p.mds)
plot(p.mds, display = "species", cex = gof/mean(gof))
points(p.mds, display = "sites", cex = gof/mean(gof), col=3)
abline(h=0, v=0, lt=2, col="grey")
mtext("Phylum", cex=.8, adj = 0)
text(1, -2.4, "Stress = 0.12")

gof <- goodness(c.mds)
plot(c.mds, display = "species", cex = gof/mean(gof))
points(c.mds, display = "sites", cex = gof/mean(gof), col=3)
abline(h=0, v=0, lt=2, col="grey")
mtext("Class", cex=.8, adj = 0)
text(3, -2.6, "Stress = 0.14")

gof <- goodness(o.mds)
plot(o.mds, display = "species", cex = gof/mean(gof))
points(o.mds, display = "sites", cex = gof/mean(gof), col=3)
abline(h=0, v=0, lt=2, col="grey")
mtext("Order", cex=.8, adj = 0)
text(-1.5, -1.3, "Stress = 0.14")

gof <- goodness(f.mds)
plot(f.mds, display = "species", cex = gof/mean(gof))
points(f.mds, display = "sites", cex = gof/mean(gof), col=3)
abline(h=0, v=0, lt=2, col="grey")
mtext("Family", cex=.8, adj = 0)
text(5,-3.5, "Stress = 0.13")

gof <- goodness(g.mds)
plot(g.mds, display = "species", cex = gof/mean(gof))
points(g.mds, display = "sites", cex = gof/mean(gof), col=3)
abline(h=0, v=0, lt=2, col="grey")
mtext("Genus", cex=.8, adj = 0)
text(6000, -2000, "Stress = 0.00")

```

Figure X. Sherperd and non-metric multidimensional scaling plot. Green oints represent samples and red points represent OTU or species. Similar samples are ordinated together. Stress values are shown at the botthom of ordination plot.

<br>



