---
title: "Transformation of taxonomy data"
---

<br>

## Taxonomy results from Phylotype-based approach

* Input file: *.cons.summary

```{r, echo=TRUE}
dir.create("../../results/tables/phylotype")
otushared = read.table(file="../../data/mothur/phylotype/qced.trim.contigs.good.unique.good.filter.unique.precluster.pick.seed.wang.pick.pick.tx.shared", stringsAsFactors=FALSE, header=T, sep='\t')
# View(otushared)

write.table(otushared, "../../results/tables/phylotype/otushared.tsv", append = FALSE, quote = FALSE, sep="\t", row.names = FALSE, col.names = TRUE)


constaxsummary = read.table(file="../../data/mothur/phylotype/qced.trim.contigs.good.unique.good.filter.unique.precluster.pick.seed.wang.pick.pick.tx.1.cons.tax.summary", stringsAsFactors=FALSE, header=T, sep='\t')
# dim(constaxsummary)
# View(constaxsummary)

write.table(constaxsummary, "../../results/tables/phylotype/constaxsummary.tsv", append = FALSE, quote = FALSE, sep="\t", row.names = FALSE, col.names = TRUE)

```



<br>


## Dataframes
* OTUs
* Extension *.a* means all data including classified and unclassified

```{r, echo=TRUE}
library(dplyr)
otushared <- otushared

phylum.a <- constaxsummary %>% filter(grepl("2", taxlevel))
phylum.a <- phylum.a[, -c(1,2,4,5)]

class.a <- constaxsummary %>% filter(grepl("3", taxlevel))
class.a <- class.a[, -c(1,2,4,5)]

order.a <- constaxsummary %>% filter(grepl("4", taxlevel))
order.a <- order.a[, -c(1,2,4,5)]

family.a <- constaxsummary %>% filter(grepl("5", taxlevel))
family.a <- family.a[, -c(1,2,4,5)]

genus.a <- constaxsummary %>% filter(grepl("6", taxlevel))
genus.a <- genus.a[, -c(1,2,4,5)]
```


<br>


## Taxon statistics: Number of rows and columns
```{r, echo=TRUE}
dim(otushared)
dim(phylum.a)
dim(class.a)
dim(order.a)
dim(family.a)
dim(genus.a)
```


<br>

## Save each taxon object to local computer
```{r, echo=TRUE}
write.table(otushared,"../../results/tables/phylotype/otushared.tsv", quote = FALSE, sep="\t",
            row.names = FALSE, col.names = TRUE)

write.table(phylum.a,"../../results/tables/phylotype/phylum.a.tsv", quote = FALSE, sep="\t",
            row.names = FALSE, col.names = TRUE)

write.table(class.a,"../../results/tables/phylotype/class.a.tsv", quote = FALSE, sep="\t",
            row.names = FALSE, col.names = TRUE)

write.table(order.a,"../../results/tables/phylotype/order.a.tsv", quote = FALSE, sep="\t",
            row.names = FALSE, col.names = TRUE)

write.table(family.a,"../../results/tables/phylotype/family.a.tsv", quote = FALSE, sep="\t",
            row.names = FALSE, col.names = TRUE)

write.table(genus.a,"../../results/tables/phylotype/genus.a.tsv", quote = FALSE, sep="\t",
            row.names = FALSE, col.names = TRUE)
```

<br>


## Remove unclassified and uncultured 
* Use filter function in dplyr package
```{r, echo=TRUE}
otu <- otushared[, -c(1,3)]
phylum <- phylum.a %>% filter(!grepl("*unclassified*|*Uncultured*|*uncultured*", taxon))
class <- class.a %>% filter(!grepl("*unclassified*|*Uncultured*|*uncultured*", taxon))
order <- order.a %>% filter(!grepl("*unclassified*|*Uncultured*|*uncultured*", taxon))
family <- family.a %>% filter(!grepl("*unclassified*|*Uncultured*|*uncultured*", taxon))
genus <- genus.a %>% filter(!grepl("*unclassified*|*Uncultured*|*uncultured*", taxon))
```

<br>

## Verify dimensions of classified only
```{r, echo=TRUE}
dim(otu)
dim(phylum)
dim(class)
dim(order)
dim(family)
dim(genus)
```

<br>

## Sort taxon nammes in ascending order
* Sorting if good when ploting grapghs
```{r, echo=TRUE}
phylum<- phylum[order(phylum$taxon),]
class<- class[order(class$taxon),]
order<- order[order(order$taxon),]
family<- family[order(family$taxon),]
genus<- genus[order(genus$taxon),]
```

<br>

## Save the filtered and sorted taxon data
```{r, echo=TRUE}
write.table(otu,"../../results/tables/phylotype/otu.tsv", quote = FALSE, sep="\t",
            row.names = FALSE, col.names = TRUE)

write.table(phylum,"../../results/tables/phylotype/phylum.tsv", quote = FALSE, sep="\t",
            row.names = FALSE, col.names = TRUE)

write.table(class,"../../results/tables/phylotype/class.tsv", quote = FALSE, sep="\t",
            row.names = FALSE, col.names = TRUE)

write.table(order,"../../results/tables/phylotype/order.tsv", quote = FALSE, sep="\t",
            row.names = FALSE, col.names = TRUE)

write.table(family,"../../results/tables/phylotype/family.tsv", quote = FALSE, sep="\t",
            row.names = FALSE, col.names = TRUE)

write.table(genus,"../../results/tables/phylotype/genus.tsv", quote = FALSE, sep="\t",
            row.names = FALSE, col.names = TRUE)
```

<br>

## Reload transformed data to update the objects
```{r}
otu <- read.table(file="../../results/tables/phylotype/otu.tsv", stringsAsFactors=FALSE, header=T, sep='\t')
phylum <- read.table(file="../../results/tables/phylotype/phylum.tsv", stringsAsFactors=FALSE, header=T, sep='\t')
class <- read.table(file="../../results/tables/phylotype/class.tsv", stringsAsFactors=FALSE, header=T, sep='\t')
order <- read.table(file="../../results/tables/phylotype/order.tsv", stringsAsFactors=FALSE, header=T, sep='\t')
family <- read.table(file="../../results/tables/phylotype/family.tsv", stringsAsFactors=FALSE, header=T, sep='\t')
genus <- read.table(file="../../results/tables/phylotype/genus.tsv", stringsAsFactors=FALSE, header=T, sep='\t')
```

<br>

## Reconfirm dimensions of reloaded data
```{r, echo=TRUE}
dim(otu)
dim(phylum)
dim(class)
dim(order)
dim(family)
dim(genus)
```

<br>

## Transpose the taxon data from column to row
* Note that the otu data are in a right formart, no transpose is necessary but we can rename the file for consistency
* Note that all samples are organized by column and the taxon by row.
* Most functions need samples organized by row so we will transpose the table
* Optionally to transpose correclty we will strip off the sample identifiers and convert them to row names so that the data matrix contains only numeric count data. This can vary greatly:)
* We will do this using *setNames* function
* Note that [,1] of transposed df will contain the sample names

```{r}
otu<-read.table(file="../../results/tables/phylotype/otu.tsv", header = TRUE, sep="\t")
rownames(otu) <- otu[,1]
otu.t <- otu[,-1]
# View(otu)
# View(otu.t)

phylum<-read.table(file="../../results/tables/phylotype/phylum.tsv", header = TRUE, sep="\t")
phylum.t = setNames(data.frame(t(phylum)), phylum[,1])
phylum.t <- phylum.t[-1,]
# View(phylum.t)

class<-read.table(file="../../results/tables/phylotype/class.tsv", header = TRUE, sep="\t")
class.t = setNames(data.frame(t(class)), class[,1])
class.t <- class.t[-1,]
# View(class.t)

order<-read.table(file="../../results/tables/phylotype/order.tsv", header = TRUE, sep="\t")
order.t = setNames(data.frame(t(order)), order[,1])
order.t <- order.t[-1,]
# View(order.t)

family<-read.table(file="../../results/tables/phylotype/family.tsv", header = TRUE, sep="\t")
family.t = setNames(data.frame(t(family)), family[,1])
family.t <- family.t[-1,]
# View(family.t)

genus<-read.table(file="../../results/tables/phylotype/genus.tsv", header = TRUE, sep="\t")
genus.t = setNames(data.frame(t(genus)), genus[,1])
genus.t <- genus.t[-1,]
# View(genus.t)

```

<br>

## Confirm dimensions of transposed data
```{r, echo=TRUE}
dim(otu.t)
dim(phylum.t)
dim(class.t)
dim(order.t)
dim(family.t)
dim(genus.t)
```

<br>

## Inspect species names
* Are there too long names that may affect ploting?
* Names should be unique. Make necessary modifiactions
```{r}
names(otu.t)
names(phylum.t)
names(class.t)
names(order.t)
names(family.t)
names(genus.t)

rownames(phylum.t)
```


<br>

### Save transposed and modified data
```{r, echo=TRUE}
write.table(otu.t,"../../results/tables/phylotype/otu.t.tsv", append = FALSE, quote = FALSE, sep="\t", eol = "\n", na = "NA", dec = ".", row.names = TRUE, col.names = TRUE, qmethod = c("escape", "double"))
write.table(phylum.t,"../../results/tables/phylotype/phylum.t.tsv", append = FALSE, quote = FALSE, sep="\t", eol = "\n", na = "NA", dec = ".", row.names = TRUE, col.names = TRUE, qmethod = c("escape", "double"))
write.table(class.t,"../../results/tables/phylotype/class.t.tsv", append = FALSE, quote = FALSE, sep="\t", eol = "\n", na = "NA", dec = ".", row.names = TRUE, col.names = TRUE, qmethod = c("escape", "double"))
write.table(order.t,"../../results/tables/phylotype/order.t.tsv", append = FALSE, quote = FALSE, sep="\t", eol = "\n", na = "NA", dec = ".", row.names = TRUE, col.names = TRUE, qmethod = c("escape", "double"))
write.table(family.t,"../../results/tables/phylotype/family.t.tsv", append = FALSE, quote = FALSE, sep="\t", eol = "\n", na = "NA", dec = ".", row.names = TRUE, col.names = TRUE, qmethod = c("escape", "double"))
write.table(genus.t,"../../results/tables/phylotype/genus.t.tsv", append = FALSE, quote = FALSE, sep="\t", eol = "\n", na = "NA", dec = ".", row.names = TRUE, col.names = TRUE, qmethod = c("escape", "double"))
```

<br>

## Reload the transformed or altered data 

```{r}
otu.t <- read.table(file="../../results/tables/phylotype/otu.t.tsv", stringsAsFactors=FALSE, header=T, sep='\t')
phylum.t <- read.table(file="../../results/tables/phylotype/phylum.t.tsv", stringsAsFactors=FALSE, header=T, sep='\t')
class.t <- read.table(file="../../results/tables/phylotype/class.t.tsv", stringsAsFactors=FALSE, header=T, sep='\t')
order.t <- read.table(file="../../results/tables/phylotype/order.t.tsv", stringsAsFactors=FALSE, header=T, sep='\t')
family.t <- read.table(file="../../results/tables/phylotype/family.t.tsv", stringsAsFactors=FALSE, header=T, sep='\t')
genus.t <- read.table(file="../../results/tables/phylotype/genus.t.tsv", stringsAsFactors=FALSE, header=T, sep='\t')
```

<br>

```{r}
# View(otu.t)
# View(phylum.t)
# View(class.t)
# View(order.t)
# View(family.t)
# View(genus.t)

# funModeling::df_status(otu.t)
# funModeling::df_status(phylum.t)
# funModeling::df_status(class.t)
# funModeling::df_status(order.t)
# funModeling::df_status(family.t)
# funModeling::df_status(genus.t)
```


<br>

## Get relative abundance
* Basically this is calculated using rowSums function
```{r, echo=TRUE}
otuprop <- otu.t/rowSums(otu.t)
phylumprop <- phylum.t/rowSums(phylum.t)
classprop <- class.t/rowSums(class.t)
orderprop <- order.t/rowSums(order.t)
familyprop <- family.t/rowSums(family.t)
genusprop <- genus.t/rowSums(genus.t)
```

<br>

## Verify dimensions of relative abundant data
```{r, echo=TRUE}
dim(otuprop)
dim(phylumprop)
dim(classprop)
dim(orderprop)
dim(familyprop)
dim(genusprop)

# View(otuprop)
# View(phylumprop)
# View(classprop)
# View(orderprop)
# View(familyprop)
# View(genusprop)
```

<br>

## Save relative abundance data
```{r, echo=TRUE}
write.table(otuprop,"../../results/tables/phylotype/otuprop.tsv", append = FALSE, quote = FALSE, sep="\t", eol = "\n", na = "NA", dec = ".", row.names = FALSE, col.names = TRUE, qmethod = c("escape", "double"))
write.table(phylumprop,"../../results/tables/phylotype/phylumprop.tsv", append = FALSE, quote = FALSE, sep="\t", eol = "\n", na = "NA", dec = ".", row.names = FALSE, col.names = TRUE, qmethod = c("escape", "double"))
write.table(classprop,"../../results/tables/phylotype/classprop.tsv", append = FALSE, quote = FALSE, sep="\t", eol = "\n", na = "NA", dec = ".", row.names = FALSE, col.names = TRUE, qmethod = c("escape", "double"))
write.table(orderprop,"../../results/tables/phylotype/orderprop.tsv", append = FALSE, quote = FALSE, sep="\t", eol = "\n", na = "NA", dec = ".", row.names = FALSE, col.names = TRUE, qmethod = c("escape", "double"))
write.table(familyprop,"../../results/tables/phylotype/familyprop.tsv", append = FALSE, quote = FALSE, sep="\t", eol = "\n", na = "NA", dec = ".", row.names = FALSE, col.names = TRUE, qmethod = c("escape", "double"))
write.table(genusprop,"../../results/tables/phylotype/genusprop.tsv", append = FALSE, quote = FALSE, sep="\t", eol = "\n", na = "NA", dec = ".", row.names = FALSE, col.names = TRUE, qmethod = c("escape", "double"))
```

<br>

## Review all dimensions of taxa data (just in case)
```{r, echo=TRUE}
cat("\n")
cat("Inludes unclassified\n")

cat("dataset\n")
cat("\n")
dim(otushared)
dim(phylum.a)
dim(class.a)
dim(order.a)
dim(family.a)
dim(genus.a)

cat("\n")
cat("Only classified\n")

cat("dataset\n")
cat("\n")
dim(phylum)
dim(class)
dim(order)
dim(family)
dim(genus)

cat("\n")
cat("Transposed\n")

cat("dataset\n")
cat("\n")
dim(otu.t)
dim(phylum.t)
dim(class.t)
dim(order.t)
dim(family.t)
dim(genus.t)

cat("\n")
cat("Relative proportions\n")

cat("dataset\n")
cat("\n")
dim(otuprop)
dim(phylumprop)
dim(classprop)
dim(orderprop)
dim(familyprop)
dim(genusprop)
```

<br><

## Create objects containing variables
* Using cbind function
* This assumes that 1st column in each file is SampleID
```{r message=FALSE, warning=FALSE}

samplemetadata <- readr::read_table2(file="../../data/metadata/samplemetadata.tsv", col_names = T)
colnames(samplemetadata)[1] <- "SampleID"

variables <- samplemetadata %>% select("SampleID", "origID", "Sex", "Time", "DayID", "DPW")
# View(variables)

otu.t.v <- otu.t
otu.t.v <- cbind(variables, otu.t)
otuprop.v <- cbind(variables, otuprop)

phylum.t.v <- phylum.t
phylum.t.v <- cbind(variables, phylum.t)
phylumprop.v <- cbind(variables, phylumprop)

class.t.v <- class.t
class.t.v <- cbind(variables, class.t)
classprop.v <- cbind(variables, classprop)

order.t.v <- order.t
order.t.v <- cbind(variables, order.t)
orderprop.v <- cbind(variables, orderprop)

family.t.v <- family.t
family.t.v <- cbind(variables, family.t)
familyprop.v <- cbind(variables, familyprop)

genus.t.v <- genus.t
genus.t.v <- cbind(variables, genus.t)
genusprop.v <- cbind(variables, genusprop)

# View(richdiv.v)
# View(phylodiv.v)
# View(otu.t.v)
# View(phylum.t.v)
# View(class.t.v)
# View(order.t.v)
# View(family.t.v)
# View(genus.t.v)
# 
# View(otuprop.v)
# View(phylumprop.v)
# View(classprop.v)
# View(orderprop.v)
# View(familyprop.v)
# View(genusprop.v)

```

<br>

## Save taxon dataframe containing variables
* Adding metadata to the dataframe facilitates analysis by groups
```{r echo=TRUE, message=FALSE, warning=FALSE, paged.print=TRUE}
write.table(otu.t.v,"../../results/tables/phylotype/otu.t.v.tsv", quote = FALSE, sep="\t",
            row.names = FALSE, col.names = TRUE)

write.table(phylum.t.v,"../../results/tables/phylotype/phylum.t.v.tsv", quote = FALSE, sep="\t",
            row.names = FALSE, col.names = TRUE)

write.table(class.t.v,"../../results/tables/phylotype/class.t.v.tsv", quote = FALSE, sep="\t",
            row.names = FALSE, col.names = TRUE)

write.table(order.t.v,"../../results/tables/phylotype/order.t.v.tsv", quote = FALSE, sep="\t",
            row.names = FALSE, col.names = TRUE)

write.table(family.t.v,"../../results/tables/phylotype/family.t.v.tsv", quote = FALSE, sep="\t",
            row.names = FALSE, col.names = TRUE)

write.table(genus.t.v,"../../results/tables/phylotype/genus.t.v.tsv", quote = FALSE, sep="\t",
            row.names = FALSE, col.names = TRUE)

# Relative data (prop)
write.table(otuprop.v,"../../results/tables/phylotype/otuprop.v.tsv", quote = FALSE, sep="\t",
            row.names = FALSE, col.names = TRUE)

write.table(phylumprop.v,"../../results/tables/phylotype/phylumprop.v.tsv", quote = FALSE, sep="\t",
            row.names = FALSE, col.names = TRUE)

write.table(classprop.v,"../../results/tables/phylotype/classprop.v.tsv", quote = FALSE, sep="\t",
            row.names = FALSE, col.names = TRUE)

write.table(orderprop.v,"../../results/tables/phylotype/orderprop.v.tsv", quote = FALSE, sep="\t",
            row.names = FALSE, col.names = TRUE)

write.table(familyprop.v,"../../results/tables/phylotype/familyprop.v.tsv", quote = FALSE, sep="\t",
            row.names = FALSE, col.names = TRUE)

write.table(genusprop.v,"../../results/tables/phylotype/genusprop.v.tsv", quote = FALSE, sep="\t",
            row.names = FALSE, col.names = TRUE)

```


}
```{r message=FALSE, warning=FALSE}

samplemetadata <- readr::read_table2(file="../../data/metadata/samplemetadata.tsv", col_names = T)
colnames(samplemetadata)[1] <- "SampleID"

# Subsetting metadata for mapping to output from dowmstream analysis
library(dplyr)
variables <- samplemetadata %>% dplyr::select("SampleID", "origID", "Sex", "Time", "DayID", "DPW")
names(variables)[2] <- "origID"
```

<br>


```{r loadtaxadata}
##all taxa data
phylum.a <- read.table(file = "../../results/tables/phylotype/phylum.a.tsv", header = TRUE, sep = "\t")
class.a <- read.table(file = "../../results/tables/phylotype/class.a.tsv", header = TRUE, sep = "\t")
order.a <- read.table(file = "../../results/tables/phylotype/order.a.tsv", header = TRUE, sep = "\t")
family.a <- read.table(file = "../../results/tables/phylotype/family.a.tsv", header = TRUE, sep = "\t")
genus.a <- read.table(file = "../../results/tables/phylotype/genus.a.tsv", header = TRUE, sep = "\t")

# otutaxonfiltered
otu <- read.table(file = "../../results/tables/phylotype/otu.tsv", header = TRUE, sep = "\t")
phylum <- read.table(file = "../../results/tables/phylotype/phylum.tsv", header = TRUE, sep = "\t")
class <- read.table(file = "../../results/tables/phylotype/class.tsv", header = TRUE, sep = "\t")
order <- read.table(file = "../../results/tables/phylotype/order.tsv", header = TRUE, sep = "\t")
family <- read.table(file = "../../results/tables/phylotype/family.tsv", header = TRUE, sep = "\t")
genus <- read.table(file = "../../results/tables/phylotype/genus.tsv", header = TRUE, sep = "\t")

# transposed
otu.t <- read.table(file = "../../results/tables/phylotype/otu.t.tsv", header = TRUE, sep = "\t")
phylum.t<- read.table(file = "../../results/tables/phylotype/phylum.t.tsv", header = TRUE, sep = "\t")
class.t <- read.table(file = "../../results/tables/phylotype/class.t.tsv", header = TRUE, sep = "\t")
order.t <- read.table(file = "../../results/tables/phylotype/order.t.tsv", header = TRUE, sep = "\t")
family.t <- read.table(file = "../../results/tables/phylotype/family.t.tsv", header = TRUE, sep = "\t")
genus.t <- read.table(file = "../../results/tables/phylotype/genus.t.tsv", header = TRUE, sep = "\t")

# with variables
otu.t.v <- read.table(file = "../../results/tables/phylotype/otu.t.v.tsv", header = TRUE, sep = "\t")
phylum.t.v<- read.table(file = "../../results/tables/phylotype/phylum.t.v.tsv", header = TRUE, sep = "\t")
class.t.v <- read.table(file = "../../results/tables/phylotype/class.t.v.tsv", header = TRUE, sep = "\t")
order.t.v <- read.table(file = "../../results/tables/phylotype/order.t.v.tsv", header = TRUE, sep = "\t")
family.t.v <- read.table(file = "../../results/tables/phylotype/family.t.v.tsv", header = TRUE, sep = "\t")
genus.t.v <- read.table(file = "../../results/tables/phylotype/genus.t.v.tsv", header = TRUE, sep = "\t")

# proportions
otuprop <- read.table(file = "../../results/tables/phylotype/otuprop.tsv", header = TRUE, sep = "\t")
phylumprop<- read.table(file = "../../results/tables/phylotype/phylumprop.tsv", header = TRUE, sep = "\t")
classprop <- read.table(file = "../../results/tables/phylotype/classprop.tsv", header = TRUE, sep = "\t")
orderprop <- read.table(file = "../../results/tables/phylotype/orderprop.tsv", header = TRUE, sep = "\t")
familyprop <- read.table(file = "../../results/tables/phylotype/familyprop.tsv", header = TRUE, sep = "\t")
genusprop <- read.table(file = "../../results/tables/phylotype/genusprop.tsv", header = TRUE, sep = "\t")

# proportions with variables
otuprop.v <- read.table(file = "../../results/tables/phylotype/otuprop.v.tsv", header = TRUE, sep = "\t")
phylumprop.v<- read.table(file = "../../results/tables/phylotype/phylumprop.v.tsv", header = TRUE, sep = "\t")
classprop.v <- read.table(file = "../../results/tables/phylotype/classprop.v.tsv", header = TRUE, sep = "\t")
orderprop.v <- read.table(file = "../../results/tables/phylotype/orderprop.v.tsv", header = TRUE, sep = "\t")
familyprop.v <- read.table(file = "../../results/tables/phylotype/familyprop.v.tsv", header = TRUE, sep = "\t")
genusprop.v <- read.table(file = "../../results/tables/phylotype/genusprop.v.tsv", header = TRUE, sep = "\t")


otu.scaled.t <- scale(otu.t) # Scale the data
p.scaled.t <- scale(phylum.t, scale = TRUE) # Scale the data
c.scaled.t <- scale(class.t, scale = TRUE) # Scale the data
o.scaled.t <- scale(order.t, scale = TRUE) # Scale the data
f.scaled.t <- scale(family.t, scale = TRUE) # Scale the data
g.scaled.t <- scale(genus.t, scale = TRUE) # Scale the data

otu.scaled.prop <- scale(otuprop) # Scale the data
p.scaled.prop <- scale(phylumprop, scale = TRUE) # Scale the data
c.scaled.prop <- scale(classprop, scale = TRUE) # Scale the data
o.scaled.prop <- scale(orderprop, scale = TRUE) # Scale the data
f.scaled.prop <- scale(familyprop, scale = TRUE) # Scale the data
g.scaled.prop <- scale(genusprop, scale = TRUE) # Scale the data


save(class, class.a, class.t, class.t.v, classprop, classprop.v, family, family.a, family.t, family.t.v, familyprop, familyprop.v, genus, genus.a, genus.t, genus.t.v, genusprop, genusprop.v, order, order.a, order.t, order.t.v, orderprop, orderprop.v, otu, otu.t, otu.t.v, otuprop, otuprop.v, phylum, phylum.a, phylum.t, phylum.t.v, phylumprop, phylumprop.v, otu.scaled.t, p.scaled.t, c.scaled.t, o.scaled.t, f.scaled.t, g.scaled.t, otu.scaled.prop, p.scaled.prop, c.scaled.prop, o.scaled.prop, f.scaled.prop, g.scaled.prop, file = "../../results/taxadata.RData")
```

<br>

```{r}
save.image("../../results/tables/phylotype/otutaxon.RData")
```


```{r include=FALSE}
sink("./sessionInfo.txt")
cat("\nSummary of session information\n\n")
sessionInfo()
sink()

sink("./LatexsessionInfo.txt")
cat("\nSummary of Latex session information\n\n")
toLatex(sessionInfo())
sink()
```

<br>
