---
title: "Progress report 1"
bibliography: /imap/library/imap.bib
date: 'Updated: `r Sys.time()`'
output:
  html_document:
    css: /imap/code/css/report.css
    # keep_md: yes
link-citations: yes
subtitle: Metadata profiling
biblio-style: apalike

---

```{r child='global_setup.Rmd'}

```


<!-- # <mark>Progress report 1</mark> -->

<br>


<!-- # Metadata profiling -->

# <!-- <br> -->
# ```{r}
# pco <- function(dis, k=2)
# {
#         tmp <-cmdscale(dis,k=k,eig=TRUE)
#         class(tmp) <- "pco"
#         return(tmp)
# }

# #############################
# #############################
# scaleFUN <- function(x) sprintf("%.0f", x)

# ```



```{r}

samplemetadata <- readr::read_table2(file="/imap/data/metadata/samplemetadata.tsv", col_names = T)
colnames(samplemetadata)[1] <- "SampleID"

metadata_status <- funModeling::df_status(samplemetadata)

# Subsetting metadata for mapping to output from dowmstream analysis
library(dplyr)
variables <- samplemetadata %>% dplyr::select("SampleID", "origID", "Sex", "Time", "DayID", "DPW")
names(variables)[2] <- "origID"
```


## Status of metadata

<hr>


```{r message=FALSE, warning=FALSE}
knitr::kable(metadata_status, "html", position = "center", booktabs = TRUE)

```

Key: **q_zeros**: quantity of zeros or missing data; **q_na**: quantity of NA; **q_inf**: quantity of infinite values; **type**: factor, character, integer or numeric..; **unique**: quantity of unique values. Percentages are indicated by **p_**.


When reviewing metadata status you may notice that numeric variables are confused with numeric data. For example, variable **DPW** (days post weaning) on Table x shows 12 missing values (3.33%) which is incorrect. As investigators we know that day 1 was coded zero (0) (12 zeros for 12 mouse) which in descriptive statistics is interpreted as missing data. To correct this we re-coded the samples with unique identifies shown as DayID to distinguish them from integers. However, depending of experiment this kind of variables need to be converted to character during analysis. 

<br>

## Samples mapped to the categorical variables

<hr>

**First 5 lines of mapping metadata**

```{r message=FALSE, warning=FALSE}
knitr::kable(head(variables, 5), "html", position = "center", booktabs = TRUE)
```

<br>


**Last 5 lines of mapping metadata**

```{r message=FALSE, warning=FALSE}
knitr::kable(tail(variables, 5), "html", position = "center", booktabs = TRUE)
```

<br>

## Frequency of experimental variables (Demo dataset)

<hr>


```{r varfreq, fig.height=8, fig.width=8, message=FALSE, warning=FALSE}
library(ggplot2)
#sort by dpw (descending)


variables <- variables[order(variables$DPW),] 

sexhistplot <- ggpubr::gghistogram(variables, x = "Sex", stat="count", fill = "#ff0000") + ggtitle("Sex variable")

timehistplot <- ggpubr::gghistogram(variables, x = "Time", stat="count", fill = "#00ff00") + ggtitle("Time variable")

# scaleFUN <- function(x) sprintf("%.0f", x)

dpwhistplot <- ggpubr::gghistogram(variables, x = "DayID", stat="count", fill = "#0000ff") + ggtitle("Days post weaning")+
  theme(axis.text.x=element_text(angle = 90, hjust = 0))+ scale_y_continuous(labels=scaleFUN)

ggpubr::ggarrange(sexhistplot,timehistplot, dpwhistplot, ncol = 1, nrow = 3,  common.legend = TRUE, legend = "top", align = "hv", labels = c(""))
```

<br>

### Frequency of experimental variables (360 samples: Case study)

<hr>


```{r varfreq_casestudy, fig.height=8, fig.width=8, message=FALSE, warning=FALSE}
library(ggplot2)
samplemetadata_casestudy <- readr::read_table2(file="/imap/data/metadata/samplemetadata_casestudy.txt", col_names = T)
colnames(samplemetadata)[1] <- "SampleID"

metadata_status <- funModeling::df_status(samplemetadata_casestudy)

# Subsetting metadata for mapping to output from dowmstream analysis
library(dplyr)
variables <- samplemetadata_casestudy %>% dplyr::select("SampleID", "origID", "Sex", "Time", "DayID", "DPW")


#sort by dpw (descending)


variables <- variables[order(variables$DPW),] 

sexhistplot <- ggpubr::gghistogram(variables, x = "Sex", stat="count", fill = "#ff0000") + ggtitle("Sex variable")

timehistplot <- ggpubr::gghistogram(variables, x = "Time", stat="count", fill = "#00ff00") + ggtitle("Time variable")

# scaleFUN <- function(x) sprintf("%.0f", x)

dpwhistplot <- ggpubr::gghistogram(variables, x = "DayID", stat="count", fill = "#0000ff") + ggtitle("Days post weaning")+
  theme(axis.text.x=element_text(angle = 90, hjust = 0))+ scale_y_continuous(labels=scaleFUN)

ggpubr::ggarrange(sexhistplot,timehistplot, dpwhistplot, ncol = 1, nrow = 3,  common.legend = TRUE, legend = "top", align = "hv", labels = c(""))
```

Figure 3. Frequency of experimental variables

<br>

### Custom variables from Bushmeat project

<hr>


```{r bushmeat, fig.height=8, fig.width=10, message=FALSE, warning=FALSE}
samplemetadata <- readr::read_table2(file="/imap/data/metadata/186samples.metadata", col_names = T)
colnames(samplemetadata)[1] <- "SampleID"

metadata_status <- funModeling::df_status(samplemetadata)

knitr::kable(metadata_status, "html", position = "center", booktabs = TRUE)




# Subsetting metadata for mapping to output from dowmstream analysis
library(dplyr)
variables <- samplemetadata %>% dplyr::select("SampleID", "Season", "Condition", "Ecosystem", "Species", "BatchNo")


seasonhistplot <- ggpubr::gghistogram(variables, x = "Season", stat="count", fill = "#ff0000") + ggtitle("") + labs(x="Season", y="Count")

condhistplot <- ggpubr::gghistogram(variables, x = "Condition", stat="count", fill = "#00ff00") + ggtitle("") + labs(x="Condition", y="Count")

ecosyhistplot <- ggpubr::gghistogram(variables, x = "Ecosystem", stat="count", fill = "#fff000") + ggtitle("") + labs(x="Ecosystem", y="Count")

spphistplot <- ggpubr::gghistogram(variables, x = "Species", stat="count", fill = "#0000ff") + ggtitle("") + theme(axis.text.x = element_text(angle = 90)) + labs(x="Animal Species", y="Count")

plots <- cowplot::align_plots(seasonhistplot, spphistplot, align = 'v', axis = 'l')
top_row <- cowplot::plot_grid(plots[[1]], condhistplot, ecosyhistplot, ncol=3, labels = "", align = 'h')
bottom_row <- cowplot::plot_grid(plots[[2]], labels = "", align = 'hv')

cowplot::plot_grid(top_row, bottom_row, ncol = 1, rel_heights = c(1.2, 1.5))

```


## Posible questions

<hr>

### Metadata profiling 

* QN1: Are there samples to be removed from the analysis based on their frequency?
* QN2: Are there enough variables for downstream diversity and statistical analysis?
* QN3: .......?
* QN4: .......?
* QN5: .......?


<br>

```{bash eval=FALSE, include=FALSE}
# Bash command

# Rscript -e "rmarkdown::render('./report3.Rmd', clean=TRUE, quiet=FALSE, output_file='report3_read_preprocessing.html', output_dir='reports')"

```

<br>
