---
title: "Progress report 1"
bibliography: ../../library/imap.bib
date: 'Updated: `r Sys.time()`'
output:
  html_document:
    css: ../../code/css/report.css
    # keep_md: yes
link-citations: yes
subtitle: Metadata profiling
biblio-style: apalike

---

```{r setup, include=FALSE}
load("./globalSetup.RData")
```

<br>



```{r include=FALSE}
samplemetadata <- readr::read_table2(file="../../data/metadata/samplemetadata.tsv", col_names = T)
colnames(samplemetadata)[1] <- "SampleID"
names(samplemetadata)

samplemetadata$SampleID <- as.factor(samplemetadata$SampleID)
samplemetadata$Var1 <- as.factor(samplemetadata$Var1)
samplemetadata$Var2 <- as.factor(samplemetadata$Var2)
samplemetadata$Var3 <- as.factor(samplemetadata$Var3)
samplemetadata$Var4 <- as.factor(samplemetadata$Var4)
#samplemetadata$Var5 <- as.factor(samplemetadata$Var5)

# You can add more variables as needed

metadatastatus <- funModeling::df_status(samplemetadata)

# Subsetting metadata for mapping to output from dowmstream analysis

library(dplyr)
variables <- samplemetadata %>% dplyr::select("SampleID", "Var1", "Var2", "Var3", "Var4")

# Confirm variable names
names(variables)

#  Define variables
variables$SampleID <- as.factor(variables$SampleID)
variables$Var1 <- as.factor(variables$Var1)
variables$Var2 <- as.factor(variables$Var2)
variables$Var3 <- as.factor(variables$Var3)
variables$Var4 <- as.factor(variables$Var4)

save(samplemetadata, variables, file = "metadatavars.RData")
```

### Optional renaming the categoric variables with meaningful names
>Example using the demo dataset located in this path: iMAP/resources/metadata/samplemetadata.tsv

```{r renamevars}
# Original names
variables %>% head(5) %>% kable()

names(variables) <- c("SampleID", "Sex", "Time", "DayID", "DPW")

# New names
variables %>% head(5) %>% kable()

```

<hr>

## Status of metadata

```{r}
varstatus <- funModeling::df_status(variables)
```

```{r message=FALSE, warning=FALSE}
library(dplyr)
# library(kableExtra)

# show data
varstatus %>% knitr::kable() 
# %>%
#   kable_styling(bootstrap_options = "striped", full_width = T)

```

Key: **q_zeros**: quantity of missing data; **p_zeros**: percentage of missing data, **q_na**: quantity of NA; **p_na**: percentage of NA, **q_inf**: quantity of infinite values; **p_inf**: percentage of infinity values,  **type**: factor, character, integer or numeric; **unique**: frequency of the values.


When reviewing metadata status you may notice that numeric variables are confused with numeric data. For example, variable **DPW** (days post weaning) on Table x shows 12 missing values (3.33%) which is incorrect. As investigators we know that day 1 was coded zero (0) (12 zeros for 12 mouse) which in descriptive statistics is interpreted as missing data. To correct this we re-coded the samples with unique identifies shown as DayID to distinguish them from integers. However, depending of experiment this kind of variables need to be converted to character during analysis. 

<br>

## Samples mapped to the categorical variables

<hr>

**First 5 lines of mapping metadata**

```{r message=FALSE, warning=FALSE}

variables %>% head(5)  %>% knitr::kable() 
# %>%
  # kable_styling(bootstrap_options = "striped", full_width = T)
```

<br>


**Last 5 lines of mapping metadata**

```{r message=FALSE, warning=FALSE}

variables %>% tail(5)  %>% knitr::kable() 
# %>%
  # kable_styling(bootstrap_options = "striped", full_width = T)
```

<br>

## Frequency of experimental variables (Demo dataset)

<hr>


```{r varfreq, fig.height=8, fig.width=8, message=FALSE, warning=FALSE}
library(ggplot2)
#sort by dpw (descending)

sexhistplot <- ggpubr::gghistogram(variables, x = "Var1", stat="count", fill = "#ff0000") + ggtitle("Sex variable")

timehistplot <- ggpubr::gghistogram(variables, x = "Var2", stat="count", fill = "#00ff00") + ggtitle("Time variable")

# scaleFUN <- function(x) sprintf("%.0f", x)

dpwhistplot <- ggpubr::gghistogram(variables, x = "Var3", stat="count", fill = "#0000ff") + ggtitle("Days post weaning")+
  theme(axis.text.x=element_text(angle = 90, hjust = 0))+ scale_y_continuous(labels=scaleFUN)

ggpubr::ggarrange(sexhistplot,timehistplot, dpwhistplot, ncol = 1, nrow = 3,  common.legend = TRUE, legend = "top", align = "hv", labels = c(""))
```

## Posible questions

<hr>

### Metadata profiling 

* QN1: Are there samples to be removed from the analysis based on their count?
* QN2: Are there enough variables for downstream diversity and statistical analysis?
* QN3: .......?
* QN4: .......?
* QN5: .......?

<br>

## Summary of packages used in the analysis
```{r}
sessionInfo()
```

<br>

